Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-06 paper/paper.tex
fix running example
hscc17

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Uncertainty Model for Quantization Error} 
\label{sec:uncertainty-model-quantization-error}

In this study, an uncertain plant model $\hat{G}(z)$ is split into two terms:
%
\begin{equation}
\label{eq:uncertainplant}
\hat{G}(z)=G(z)+\Delta{G(z)},
\end{equation}

\noindent where $G(z)$ is the discretized nominal plant model and
$\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
uncertainties~\cite{Bessa16}.  Here, an uncertainty model to accommodate the
quantization noise effects on $\hat{G}(z)$ is proposed.  As a result,
Eq.~\eqref{eq:uncertainplant} is rewritten as
%
\begin{equation}
\label{eq:uncertainFWLplant}
\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}+\Delta{G_{P}(z)},
\end{equation}

@@

  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (y);
  \path  
   (circle.east) edge (switch1)
   (switch2) edge (q1.west)
   (q1.east) edge (cz.west)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (gs.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Sampled System. \label{fig:sampledsystem}}
\end{figure}

@@

For this particular example, the actual implementation of $C(z)$ using
\param{20}{20} implementation format can be represented by the following
z-expression:

\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{4.00888156890869140625z^2{-}0.00041961669921875z
-0.000213623046875}{-0.003753662109375z^2{+}7.37355804443359375z-7.2847900390625},$
}
\end{equation}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Modelling Errors}

In this section, we show how to embed discretisation errors on the plant model, as follows: 
%$\hat{G}(z)$ is split into two terms:
%
\begin{equation}
\label{eq:uncertainplant}
%\hat{G}(z)=G(z)+\Delta{G(z)},
\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
\end{equation}
where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$,

\noindent where $G(z)$ is the discretized nominal plant model and
$\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
uncertainties~\cite{Bessa16}.

\subsection{A Uncertainty Model for Quantization Error} 
\label{sec:uncertainty-model-quantization-error}

Here, an uncertainty model to accommodate the
quantization noise effects on $\hat{G}(z)$ is proposed.  As a result,
Eq.~\eqref{eq:uncertainplant} is rewritten as
%
\begin{equation}
\label{eq:uncertainFWLplant}
\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}+\Delta{G_{P}(z)},
\end{equation}

@@

  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (y);
  \path  
   (circle.east) edge (switch1)
   (switch2) edge (q1.west)
   (q1.east) edge (cz.west)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (gs.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Sampled System. \label{fig:sampledsystem} \red{[Please update this figure: reference enters downstream of control block. Clarify signals over lines in plot.]}}
\end{figure}

@@

For this particular example, the actual implementation of $C(z)$ using
\param{4}{16} implementation format can be represented by the following
z-expression:

\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
}
\end{equation}
